GEE models

### 2017-07-11 doc/manuscript.Rmd
removed top outline and added set_options

<!-- outline

TODO:
- Bootstrap for the longitudinal table data... like instead of an ANOVA/GEE for
the p-value...?
- What about adiponectin?
- Precise followup time for each participant?
- [X] Interaction by sex or ethnicity
- [X] Interaction by time
- [X] Sensitivity analysis with TAG
- [X] PLS-DA with dysglycemia (for anyone who got it over the years).
- [X] Replace TAG with BaseTAG in the QIC (or use both)
- [X] Fix time axis labels on LCMM plot
- Describe LCMM and PLS-DA better in plots
- [X] Use pct for PLSDA
- [X] Explained variation in X and in Y for PLS-DA
- Supplemental only file (separate from manuscript).. maybe?

-->

```{r setup, echo=FALSE}
devtools::load_all('.')
```

>>>>

```{r setup, echo=FALSE}
devtools::load_all('.')
set_options()
```
